Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-07 longSC.tex
final to PC

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
                \end{center}
        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5_0}
\end{figure*}

@@

We list here the important findings from the model comparisons:
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

@@

\begin{figure}[p]
             \begin{center}
              %\resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
              \end{center}
             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_8}
\end{figure}

\begin{figure}[p]
             \begin{center}
              %\resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
              \end{center}
             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_9}
\end{figure}

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
As it has been discussed in Sec~\ref{sec:theory_loworder}, NSC(3,2) is underestimated by the hydrodynamic calculations. 
The hydrodynamic calculations show very weak $p_{\rm T}$ dependence for NSC(3,2) and a moderate $p_{\rm T}$ dependence for NSC(4,2).
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations except for the centrality range 40-50\% where the correlation strength gets stronger with increasing $p_{\rm T}$. 
In the case of NSC(4,2), the $p_{\rm T}$ dependence is well described in all centrality ranges.

>>>>

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
                \end{center}
        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5_0}
\end{figure*}

@@

We list here the important findings from the model comparisons:
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of the centrality ranges while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

@@

\begin{figure}[p]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
              \end{center}
             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_8}
\end{figure}

\begin{figure}[p]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
              \end{center}
             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_9}
\end{figure}

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% centrality range where the data shows stronger $p_{\rm T}$ dependence than the models. The difference of the model calculation between two parametrizations is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centrality range and underestimate in the centrality range $>$20\%. However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities. 
While the difference of the model calculations between two parametrizations in most of the centrality ranges is rather small, the clear separation between two parametrizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
